Addendum to a survey of HTTP caching on the Semantic Web

### 2015-03-20 sanity/report.tex
Introduction
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1106 43ef1190-90fd-4dd7-a769-d0121f02b80e

\usepackage[english,british]{babel}
%\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{appendix}

@@

\title{A survey of HTTP caching implementations on the open Semantic Web}
\author{Kjetil Kjernsmo}
\institute{Department of Informatics,
Postboks 1080 Blindern,
N-0316 Oslo, Norway \email{kjetil@kjernsmo.net}}

@@

@@

The Billion Triple Challenge 2014 dataset provided data in the form of
NQuad files. Due to the presence of invalid RDF, we iterated through
the NQuad files on a line-by-line basis. First, we matched each line
against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework
RDF::Trine\footnote{https://metacpan.org/release/GWILLIAMS/RDF-Trine-1.011}
was used to parse the line. Lines that failed to parse were
discarded. We have not investigated whether this could introduce
biases. Statements were then accepted into a new NQuad file if they
had a predicate that matched the \rdfterm{sd:endpoint} or matched a
case-insensitive regular expression \texttt{sparql} if the subject and
objects were both resources, or the predicates
\rdfterm{void:vocabulary}, \rdfterm{rdfa:vocabulary}, or
\rdfterm{api:vocabulary}, as well as having a resource as
object. Finally, statements with the the classes
\rdfterm{cogs:Endpoint}, \rdfterm{owl:Ontology} and
\rdfterm{voaf:Vocabulary} in the object position were also
accepted\footnote{LOV may be used to resolve these prefixed
  names}. More classes and properties were considered, but not used in
the data reduction if they did not occur in the original data.

@@

Finally, if the LOV SPARQL endpoint used a URI for the vocabulary that
was different from the namespace URI (after a normalization step),
another request would be made to record the selected HTTP headers from
that as well.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs}

>>>>

\documentclass{article}
\usepackage[english,british]{babel}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{hyperref}

@@

\title{Addendum to a survey of HTTP caching on the Semantic Web}
\author{Kjetil Kjernsmo}

@@

This Technical Report is an addendum to a paper to be published in the
proceedings of the Extended Semantic Web Conference 2015 titled ``A
survey of HTTP caching implementations on the open Semantic Web''.

That paper was motivated from the perception that we had that caching
was much used on the open Semantic Web. This is surprising, since
caching has been given a very prominent role in the architecture of
the World Wide Web, and caching based on HTTP headers as defined in
RFC7234 \cite{rfc7234} and RFC7232 \cite{rfc7232} is prevalent
elsewhere in the Web.

To understand the actual usage, we conducted an extensive survey of
actual resources on the Semantic Web. We obtained data from different
sources, with the breadth of the Semantic Web mainly covered by the
Billion Triple Challenge (BTC) 2014 dataset  \cite{btc-2014}.

In this addendum, we document in detail several aspects that there
were not sufficient space for in the conference paper. Since we made
the assumption that the relevant headers are mostly the same for each
host, Section~\ref{app:reduction} documents how the large BTC2014 data
set is reduced to visit a large number hosts, but a small number of
resources. Then, Section~\ref{app:fetcher} discusses the system we
developed to visit these resources and extract the information that we
were interested. Section~\ref{app:stats} documents our main
statistical method and Section~\ref{app:qqplot} has an analysis of
valid versus invalid responses.

@@

The BTC2014 dataset provided data in the form of NQuad files. Due to
the presence of invalid RDF, we iterated through the NQuad files on a
line-by-line basis. First, we matched each line against a regular
expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework
RDF::Trine\footnote{https://metacpan.org/release/GWILLIAMS/RDF-Trine-1.011}
was used to parse the line. Lines that failed to parse were
discarded. We have not investigated whether this could introduce
biases. Statements were then accepted into a new NQuad file if they
had a predicate that matched the \rdfterm{sd:endpoint} or matched a
case-insensitive regular expression \texttt{sparql} if the subject and
objects were both resources, or the predicates
\rdfterm{void:vocabulary}, \rdfterm{rdfa:vocabulary}, or
\rdfterm{api:vocabulary}, as well as having a resource as
object. Finally, statements with the the classes
\rdfterm{cogs:Endpoint}, \rdfterm{owl:Ontology} and
\rdfterm{voaf:Vocabulary} in the object position were also
accepted\footnote{Linked Open Vocabularies \cite{lov2} may be used to
  resolve these prefixed names}. More classes and properties were
considered, but not used in the data reduction if they did not occur
in the original data.

@@

Finally, if the Linked Open Vocabularies \cite{lov2} SPARQL endpoint
used a URI for the vocabulary that was different from the namespace
URI (after a normalization step), another request would be made to
record the selected HTTP headers from that as well.

@@

\section{Valid versus invalid responses}\label{app:qqplot}

%\bibliographystyle{plain}
\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs}
